Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-16 robdml.tex
p2

\textbf{Deep Metric Learning.}
%
A wide range of applications such as image retrieval~\cite{imagesim2},
cross-modal retrieval~\cite{ladderloss}, and face recognition~\cite{facenet}
can be formulated as DML problem.
%
A well-designed loss function and a proper sampling method are crucial for DML
performance~\cite{dmlreality}.  For instance, the classical
triplet loss~\cite{facenet} could reach state-of-the-art performance with an appropriate
sampling strategy~\cite{revisiting}.

>>>>

\textbf{Deep Metric Learning.}
%
A wide range of applications such as image retrieval~\cite{imagesim2},
cross-modal retrieval~\cite{ladderloss}, and face recognition~\cite{facenet}
can be formulated as a DML problem.
%
A well-designed loss function and a proper sampling method are crucial for DML
performance~\cite{dmlreality}.  For instance, the classical
triplet loss~\cite{facenet} could reach state-of-the-art performance with an appropriate
sampling strategy~\cite{revisiting}.
